A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-30 writeup/paper.tex
Modified the discussion section

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{final-figures/quality-scatter}
\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 295,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Discussion}
MTurk has a strong and diverse presence of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. Although unfiltered data can contain large amounts of noise, crowdsourced pipelines, which contain human oversight as a means of evaluation, offer a feasible way of ensuring high quality data, even on tasks which require more complex labels. While MTurk does offer the ability to restrict workers based on country, embedded per-task controls which are checked either automatically when possible, or manually in a second-pass HIT, are likely to provide higher quality data than naive demographic filters.

Although our research targeted bilingual workers on Mechanical Turk, and neglected monolingual workers, we believe our results reliably represent the current speaker populations, since the vast majority of the work available on the crowdsourced platform is currently English-only.  We therefore assume the number of non-English speakers is small.  In the future, it may be desirable to recruit monolingual foreign workers.  In such cases, we recommend other tests to validate their language abilities in place of our translation test.  These could include performing narrative cloze, or listening to audio files containing speech in different language and identifying their language.

>>>>

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=.8\linewidth]{final-figures/quality-scatter}
\end{center}

\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 295,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Discussion}
The Mechanical Turk gives research access to a diverse set of bilingual workers, making it a promising resource for researchers and developers of multilingual systems. 
Although unfiltered data can contain large amounts of noise, 
a variety of techniques can be incorporated into crowdsourcing pipelines to ensure high quality data.  Based on our study, we suggest restricting workers to countries that plausibly speak the foreign language of interest, and embedding gold standard controls where possible, rather than relying solely on self-reported language skills.

Although our study targeted bilingual workers on Mechanical Turk, and neglected monolingual workers, we believe our results reliably represent the current speaker populations, since the vast majority of the work available on the crowdsourced platform is currently English-only.  We therefore assume the number of non-English speakers is small.  In the future, it may be desirable to recruit monolingual foreign workers.  In such cases, we recommend other tests to validate their language abilities in place of our translation test.  These could include performing narrative cloze, or listening to audio files containing speech in different language and identifying their language.

\section{Data release}

We plan to release all data used in this study upon publication of this paper.  Our data release will include the raw data, along with bilingual dictionaries that are filtered to be high quality.
